\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
fixed intro

\begin{abstract}
In unknown or changing environments such as warehouses for consumer goods, robots may need to quickly plan grasps on previously unknown objects.
Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
In this paper, we show that framing grasp planning as a multi-armed bandit problem, a standard framework for making sequential descisions, provides a principled way to quickly select a grasp from a set of candidates on an uncertain shape.
We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of T versus planning grasps using existing methods.
\end{abstract}

@@

\todo{ref figure}

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp. You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
\vspace*{-10pt}
\label{fig:sampling_convergence}
\end{figure}

>>>>

\begin{abstract}
In unknown or changing environments such as warehouses for consumer goods, robots may need to quickly plan grasps on previously unknown objects.
Due to sensor noise, occlusions, and surface properties such as transparency and specularity, it may be difficult to plan successful grasps.
Planning grasps in the presence of uncertainty can be computationally demanding because fully evaluating the expected quality of even a single grasp may require a large number of samples.
In this paper, we show that framing grasp planning as a multi-armed bandit problem, a standard framework for making sequential descisions, provides a principled way to quickly select a grasp from a set of candidates on an uncertain shape.
We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS), which can be especially computationally demanding.
We utilize successive elimination to solve a multi-armed bandit problem and show a speedup of 10x versus planning grasps using existing methods.
\end{abstract}

@@

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation and use those to efficiently sample from the GPIS for grasp quality evaluation, which reduces computational complexity of sampling from $O(n^6)$ to $O(n^3)$ for a 2D $n \times n$ workspace. Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.

@@
